Generalized spaces for constructive algebra

### 2023-09-12 slides-herrsching2019.tex
Gelfand duality and several smaller items
typo

    In verifying the fundamental theorem of Galois theory, at some point one
    has to extend a given~$k$-homomorphism~$E \to L$ which is defined on some
    finite intermediate extension~$E$ to~$L$. One-step extensions to larger
    intermediate extensions are no problem, but extending to all of~$L$
    requires some form of choice. By passing from the topological Galois group
    to its localic group, this issue vanishes. References include the papers
    \fixedhref{https://core.ac.uk/download/pdf/82660137.pdf}{Galois theory in a topos} and
    \fixedhref{http://www.numdam.org/article/CTGDC_1981__22_1_61_0.pdf}{Localic groups} by Gavin Wraith.
    Olivia Caramello's paper
    \fixedhref{https://arxiv.org/abs/1301.0300}{Topological galois theory} is
    also relevant.

@@

  \jnote{2}{
    \textbf{Example.} The theory of rings has:
    \begin{enumerate}
      \item one sort: $R$
      \item five constant symbols: $0$ and $1$ (nullary), $-$ (unary), $+$ and
      $\cdot$ (binary)
      \item no relation symbols
      \item the usual axioms, such as $\top \vdash_{x:R,y:R} x + y = y + x$
    \end{enumerate}

>>>>

    In verifying the fundamental theorem of Galois theory, at some point one
    has to extend a given~$k$-homomorphism~$E \to L$ which is defined on some
    finite intermediate extension~$E$ to~$L$. One-step extensions to larger
    intermediate extensions are no problem, but extending to all of~$L$
    requires some form of choice. By passing from the topological Galois group
    to its localic group, this issue vanishes. References include the papers
    \fixedhref{https://core.ac.uk/download/pdf/82660137.pdf}{Galois theory in a topos} and
    \fixedhref{http://www.numdam.org/article/CTGDC_1981__22_1_61_0.pdf}{Localic groups} by Gavin Wraith.
    Olivia Caramello's paper
    \fixedhref{https://arxiv.org/abs/1301.0300}{Topological Galois theory} is
    also relevant.

@@

  \jnote{2}{
    \textbf{Example.} The theory of rings has:
    \begin{enumerate}
      \item one sort: $R$
      \item five function symbols: $0$ and $1$ (nullary), $-$ (unary), $+$ and
      $\cdot$ (binary)
      \item no relation symbols
      \item the usual axioms, such as $\top \vdash_{x:R,y:R} x + y = y + x$
    \end{enumerate}
